Bacterial Microbiome and Obesity Meta-analysis Supplemental

### 2016-03-20 Sze_ObesityMicrobiomeMetaNoMetaHit_PeerJ_2016.Rmd
Manuscript power and sequence sim update

demographics <- read.csv("results/tables/denovodemographicsTable.csv")
OverallPValue <- read.csv("results/tables/denovoOverallPTable.csv")
ShannonRRTable <- read.csv("results/tables/denovoShannonRRTable.csv")
BFRatioRRTable <- read.csv("results/tables/denovoBFRatioRRTable.csv")
ZScoreCombinedData <- read.csv("results/tables/denovoCombinedData.csv")
ZScoreTurnbaughData <- read.csv("results/tables/denovoTurnbaughData.csv")
AUCRFData <- read.csv("results/tables/denovoAUCRFDataTable.csv")
PowerTable <- read.csv("results/tables/denovoPowerTable.csv")

```{r install_needed_packages, echo=FALSE, message=FALSE, warning=FALSE}
deps = c("knitr","vegan","epiR","AUCRF","meta","metafor","ggplot2", "plyr", "reshape2", "RColorBrewer", "scales", "gridExtra");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}

@@

Study <- as.character(PowerTable$Study)
PowerH <- PowerTable$StudyPowerH
PowerBF <- PowerTable$StudyPowerBF

table4 <- cbind(Study, PowerH, PowerBF)
colnames(table4) <- c("Study", "Shannon Diversity Power (%)", "B/F Ratio Power (%)")

@@

>>>>

demographics <- read.csv("results/tables/denovodemographicsTable.csv")
OverallPValue <- read.csv("results/tables/denovoOverallPTable.csv")
ShannonRRTable <- read.csv("results/tables/denovoShannonRRTable.csv")
BFRatioRRTable <- read.csv("results/tables/denovoBFRatioRRTable.csv")
ZScoreCombinedData <- read.csv("results/tables/denovoCombinedData.csv")
ZScoreTurnbaughData <- read.csv("results/tables/denovoTurnbaughData.csv")
AUCRFData <- read.csv("results/tables/denovoAUCRFDataTable.csv")
PowerTable <- read.csv("results/tables/denovoPowerTable.csv")
ModelledPowerH <- read.csv("results/tables/denovoModelledPowerH.csv")
ModelledPowerBF <- read.csv("results/tables/denovoModelledPowerBF.csv")
```

```{r install_needed_packages, echo=FALSE, message=FALSE, warning=FALSE}
deps = c("knitr","vegan","epiR","AUCRF","meta","metafor","ggplot2", "plyr", "reshape2", "RColorBrewer", "scales", "gridExtra", "pwr", "statmod");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}

@@

Study <- c(as.character(PowerTable$Study))
PowerH <- c(PowerTable$StudyPowerH)
GroupsOposH <- c(ShannonRRTable$tposH + ShannonRRTable$cposH)
GroupsNonOposH <- c(ShannonRRTable$tnegH + ShannonRRTable$cnegH)
GroupsH <- paste(GroupsOposH, "|", GroupsNonOposH, sep="")

PowerHRR <- c(PowerTable$StudyPowerHRR)
GroupsLowH <- c(format(round(ShannonRRTable$tposH / (ShannonRRTable$tposH + ShannonRRTable$tnegH), 1), nsmall=1))
GroupsHighH <- c(format(round(ShannonRRTable$cposH / (ShannonRRTable$cposH + ShannonRRTable$cnegH), 1), nsmall=1))
GroupsHRR <- paste(GroupsLowH, "|", GroupsHighH, sep="")

PowerBF <- c(PowerTable$StudyPowerBF)
GroupsOposBF <- c(BFRatioRRTable$tposBF + BFRatioRRTable$cposBF)
GroupsNonOposBF <- c(BFRatioRRTable$tnegBF + BFRatioRRTable$cnegBF)
GroupsBF <- paste(GroupsOposBF, "|", GroupsNonOposBF, sep="")

PowerBFRR <-c(PowerTable$StudyPowerBFRR)
GroupsLowBF <- c(format(round(BFRatioRRTable$tposBF / (BFRatioRRTable$tposBF + BFRatioRRTable$tnegBF), 1), nsmall=1))
GroupsHighBF <- c(format(round(BFRatioRRTable$cposBF / (BFRatioRRTable$cposBF + BFRatioRRTable$cnegBF), 1), nsmall=1))
GroupsBFRR <- paste(GroupsLowBF, "|", GroupsHighBF, sep="")

table4 <- cbind(Study, PowerH, GroupsH, PowerHRR, GroupsHRR, PowerBF, GroupsBF, PowerBFRR, GroupsBFRR)
colnames(table4) <- c("Study", "Shannon Diversity Power (%)", "Group n (Obese|Non-Obese)", "Shannon RR Power (%)", "Group Proportion (Low|High)", "B/F Ratio Power (%)", "Group n (Obese|Non-Obese)", "B/F ratio RR (%)", "Group Proportion (Low|High)")

@@

**Table 5. Summary of Power Calculations Simulations for Shannon Diversity for Non-obese versus Obese**

```{r Table_5, echo=FALSE, message=FALSE, warning=FALSE}

table5 <- ModelledPowerH[, -1]

colnames(table5) <- c("Estimated Power for 1% Difference", "Estimated Power for 5% Difference", "Estimated Power for 10% Difference", "Estimated Power for 15% Difference", "Actual % Difference", "Study")

kable(table5, format = "markdown", align = 'c', padding = 2)

**Table 6. Summary of Power Calculations Simulations for B/F ratio for Non-obese versus Obese**

```{r Table_6, echo=FALSE, message=FALSE, warning=FALSE}

table6 <- ModelledPowerBF[, -1]

colnames(table6) <- c("Estimated Power for 1% Difference", "Estimated Power for 5% Difference", "Estimated Power for 10% Difference", "Estimated Power for 15% Difference", "Actual % Difference", "Study")

kable(table6, format = "markdown", align = 'c', padding = 2)
```

### 2016-03-20 microbiomeAndobesitySupplemental.Rmd
Manuscript power and sequence sim update

```{r Table_1, echo=FALSE, message=FALSE, warning=FALSE}

@@

>>>>

```{r Table_S1, echo=FALSE, message=FALSE, warning=FALSE}

@@

**Table S2. Top Sequence Similarity by Variable Region Based on the Representative OTU for Clostridiales, Lachnospiraceae, and Ruminococcaceae**

```{r Table_S2, echo=FALSE, message=FALSE, warning=FALSE}

VariableRegion <- c("V1-V2 vs V2", "V1-V3", "V4")

TopHitClos <- c("None", "45.2 | 45.2 | 46.5", "60.9 | 60.9 | 32.8")
AverageClos <- c("None", "34.6 | 34.6 | 59.4", "58.9 | 58.9 | 33.2")
TopHitLachno <- c("TBC", "40.7 | 40.7 | 50", "61.3 | 61.3 | 32.8")
AverageLachno <- c("TBC", "37.9 | 37.9 | 52.1", "59.4 | 59.4 | 33.1")
TopHitRumi <- c("TBC", "15.5 | 15.5 | 84.1", "60.5 | 60.5 | 32.8")
AverageRumi <- c("TBC", "15.2 | 15.2 | 84.1", "57.5 | 57.5 | 33.2")

table2 <- cbind(VariableRegion, TopHitClos, AverageClos, TopHitLachno, AverageLachno, TopHitRumi, AverageRumi)
colnames(table2) <- c("Variable Region", "Top Similarity Colstridiales (Id | Sim | Gaps)", "Average Similarity Colstridiales (Id | Sim | Gaps)", "Top Similarity Lachnospiraceae (Id | Sim | Gaps)", "Average Similarity Lachnospiraceae (Id | Sim | Gaps)", "Top Similarity Ruminococcaceae (Id | Sim | Gaps)", "Average Similarity Ruminococcaceae (Id | Sim | Gaps)")

kable(table2, format = "markdown", align = 'c', padding = 2)

```
